### 2023-10-10 letters/cover letter-fdarecurrent-rd2.tex
Update the files for accepted version

\opening{Dear Drs. Jones and Liang:}

Kindly find enclosed the manuscript titled ``Recurrent Event Analysis in the Presence of Real-time High Frequency Data via Random Subsampling.''  This manuscript is motivated by digital monitoring studies that collect real-time high frequency data via mobile sensors and their use in the analysis of recurrent event outcomes such as smoking, drug use, alcohol use, or self-identified moments of suicide ideation. Likelihood calculations for the recurrent event analysis become computationally prohibitive in this setting. A random subsampling framework is proposed for computationally efficient, approximate likelihood-based estimation which is shown to be equivalent to penalized logistic regression estimation, allowing for standard, ``off-the-shelf'' software to be used in fitting these models. Simulations demonstrate the method and efficiency-computation trade-off. We end by illustrating our approach using data from a digital monitoring study of suicidal ideation.

We believe the work presents an important advance in how researchers should approach recurrent event analysis in settings in the present of real-time high frequency data such as in mobile health where sensor data is prevalent.

Thank you for your consideration. We look forward to hearing back from you.

>>>>

\opening{Dear Dr. Liang:}

We thank you for the positive news regarding our manuscript ID JCGS-22-236, "Recurrent event analysis in the presence of real-time high frequency data via random subsampling."   We have revised the article to address the referee's remaining comment.  The report had a final comment about Section 5.2. Specifically, it asked about the suitability of relative MISE as a more useful indicator when selecting Delta rather than AIC. The new version complies with this request by adding a sentence regarding this issue in Section 5.2.

Thank you again for the positive news regarding our manuscript.  We look forward to seeing our work in the Journal of Computational and Graphical Statistics.
